
---
title: "DEER Project DEER VIT Status Update"
output:
  pdf_document:
    dev: png
  html_document: null
  word_document: null
params:
  tabby: tabby
---
\pdfminorversion=5 
\pdfcompresslevel=9
\pdfobjcompresslevel=2
```{r,echo=F,include=FALSE}
pdf.options(useDingbats = TRUE,compress=T)
library(knitr)
library(jpeg)


tabby<-readRDS(params$tabby)

```
This is an automated updated for the DEER Project. Results reported within this document are running on the following scripts:\vspace{5mm}

\large\textbf {Report Date: `r format(Sys.time(), '%d %B, %Y  %H:%M')`}
\vspace{10mm}

\large\textbf {Birth Freqs}
```{r,echo=F,warning=FALSE}
tabby$Serial<-as.character(tabby$Serial)
tabby$`Mom Freq`<-as.character(tabby$`Mom Freq`)
tabby$`VIT Freq`<-as.character(tabby$`VIT Freq`)

tabby$CurrentVitStatus<-ifelse(tabby$CurrentVitStatus=='Birth Not yet triggered','BNYT',
                     ifelse(tabby$CurrentVitStatus=='Birth-triggered by light and temperature', 'B_Sensor',
                                           ifelse(tabby$CurrentVitStatus=='Birth-triggered by temperature','B_Sensor',
                                                  ifelse(tabby$CurrentVitStatus=='Birth-triggered by light','Birth_Sensor',ifelse(tabby$CurrentVitStatus=='Birth-triggered by lack of comm','B_Comm',
                                                                                                                                  ifelse(tabby$CurrentVitStatus == 'No Status','No Status',NA))))))

tabl<-tabby[,c(1,2,3,4,5,6,9,13)]
colnames(tabl)<-c('Serial','MomFreq','#Fetus','VitFreq','SC','SC3Day','VitStat','Dist')
tabl<-tabl[order(tabl$MomFreq,decreasing=F),]



tabl1<-tabl[which(!(tabl$VitStat=='BNYT')),]
tabl1<-tabl1[which(!(tabl1$VitStat=='No Status')),]


kable(tabl1,format='markdown',row.names=F,align='c',digits=2,padding=0,caption='Birth Freqs')

```

\vspace{1mm}

\large\textbf {Birth Data}
```{r,echo=F,warning=FALSE}

tabl3<-tabby[,c(2,7,8,11,12,10,9)]
colnames(tabl3)<-c('MomFreq','E_East','E_North','M_East','M_North','LastDate','VitStat')
tabl3<-tabl3[order(tabl3$MomFreq,decreasing=F),]



tabl3<-tabl3[which(!(tabl3$VitStat=='BNYT')),]
tabl3<-tabl3[which(!(tabl3$VitStat=='No Status')),]

tabl3<-tabl3[,-7]

tabl3$E_East<-floor(tabl3$E_East)
tabl3$E_North<-floor(tabl3$E_North)
tabl3$M_East<-floor(tabl3$M_East)
tabl3$M_North<-floor(tabl3$M_North)

kable(tabl3,format='markdown',row.names=F,align='c',digits=2,padding=0,caption='Birth Data')

```

\vspace{1mm}

\clearpage

\large\textbf {Non-Birth Freqs}
```{r,echo=F,warning=FALSE}
tabl2<-tabl[which(tabl$VitStat=='BNYT'|tabl$VitStat=='No Status'),]
kable(tabl2,format='markdown',row.names=F,align='c',digits=2,padding=0,caption='Non Birth Freqs')

```